\documentclass[12pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath,amssymb}
\usepackage{hyperref}
\usepackage{geometry}
\geometry{margin=2.5cm}

\title{Das VEGA INFINITE AEEA CONTINUUM: A Conceptual Framework}
\author{ADAM EREN VEGA – Æ – \\ (Erenşah Kaygusuz, Germany)}
\date{2025}

\begin{document}
\maketitle

\begin{abstract}
This work introduces Das VEGA INFINITE AEEA CONTINUUM as a new conceptual framework within the Resonance Data and QIRC paradigm. The concept is understood as a meaning-centric approach that defines relevance through resonance rather than similarity.
\end{abstract}

\section{Introduction}
Das VEGA INFINITE AEEA CONTINUUM addresses a central gap in current AI research: the inability to model meaning as a dynamic, time-dependent state. This concept is embedded in the Vega Continuum.

\section{Definition of Das VEGA INFINITE AEEA CONTINUUM}
Das VEGA INFINITE AEEA CONTINUUM is a conceptual framework that models meaning not as a static point, but as a resonant state with temporal coherence.

\section{What This Is}
Das VEGA INFINITE AEEA CONTINUUM is a theoretical framework for structuring meaning in artificial systems. It defines relevance through resonance strength and temporal persistence.

\section{What This Is NOT}
Das VEGA INFINITE AEEA CONTINUUM is NOT: an algorithm, an implementation, a database, a product, a patent claim for new physics or quantum hardware.

\section{Relationship to Resonance Data and QIRC}
Das VEGA INFINITE AEEA CONTINUUM extends the foundations of Resonance Data and Quantum-Inspired Resonance Computing (QIRC) by formalizing specific aspects of meaning representation.

\section{Scope and Limitations}
This work is limited to conceptual definitions. No implementation details, algorithms, or operational architectures are disclosed.

\section{Conclusion}
Das VEGA INFINITE AEEA CONTINUUM contributes to foundational research in meaning-centric AI systems. It establishes prior art without operational disclosure.

\section*{Legal Notice}
\copyright\ 2025 ADAM EREN VEGA – Æ –. All rights reserved.\\
License: Creative Commons Attribution 4.0 International (CC BY 4.0)\\
This work is part of the Vega Continuum research framework.\\
All concepts and terminology are attributed to the author unless otherwise cited.

\end{document}
